Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-29 PNAS/index.Rnw
Fix sig figs and other minor issues

If the blade cuts and the wire edge are scanned at a resolution of $\Sexpr{res*1000} \mu m$, the resulting digital files will require $\Sexpr{ncomp_max}$ comparisons per blade cut, or $\Sexpr{ncomp_max*2}$ comparisons overall.
These comparisons are required in order to find the optimal alignment between the wire and the blade cut; they are implicit in the calculation of cross-correlation which is either the first step or the only step used to objectively assess the similarity between striated evidence such as bullets, aperture shear, and firing pin impressions.
This problem is not unique to algorithms, however; and examiner would need to physically align the wire and the blade cut by searching along the length of the cut to visually match striations, performing the same process physically that the algorithm performs computationally.
While these sequential comparisons are of course highly autocorrelated, and we cannot assume sequential independence when calculating the probability of an error, they serve as an upper bound on the number of comparisons which could be performed.

>>>>

If the blade cuts and the wire edge are scanned at a resolution of $\Sexpr{res*1000} \mu m$, the resulting digital files will require \svp{approximately $\Sexpr{format(round(ncomp_max/1000)*1000, big.mark=',')}$ comparisons per blade cut; $\Sexpr{format(round(ncomp_max/1000)*2000, big.mark=',')}$ comparisons overall}.
These comparisons are required in order to find the optimal alignment between the wire and the blade cut; they are implicit in the calculation of cross-correlation which is either the first step or the only step used to objectively assess the similarity between striated evidence such as bullets, aperture shear, and firing pin impressions.
This problem is not unique to algorithms, however; and examiner would need to physically align the wire and the blade cut by searching along the length of the cut to visually match striations, performing the same process physically that the algorithm performs computationally.
While these sequential comparisons are of course highly autocorrelated, and we cannot assume sequential independence when calculating the probability of an error, they serve as an upper bound on the number of comparisons which could be performed.
